\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-03-21 paper/main.tex
Fixed underline
minor
Removed fix
polishing conclusions

\subsection{Usage}
\label{sec:usage}

@@

The following script runs FreeFuzz all bugs associated with version
2.2.0 of \torch.  The command \CodeIn{run-tool} takes the library
version as an input, along with the name of the docker container
(already created), the name of the library, and the user-provided
script containing the commands to run the tool
(\CodeIn{run\_freefuzz\_docker.sh}. The script reports on output how
many bugs are reproducible with this library version were successfully
reproduced by the given tool.  Tool execution proceeds as
follows. First, a Docker container associated with the tool is created using
\CodeIn{install_freefuzz_docker.sh}. Next, a reproducible bug is tested using
the specified library version as input to verify the setup.
Following this, the preprocessing script (\CodeIn{preprocess.py}) is executed 
to extract error types and identify buggy APIs for the given library version.
The environment inside the Docker container is then updated to match the specified version, 
ensuring compatibility before running the fuzzing tool. Once execution is complete, a postprocessing 
script (\CodeIn{postprocess.py}) is run to analyze the execution log against the ground truth, 
determining whether the bugs were successfully reproduced.

@@

\Fix{Abid: Added text to motivate adding support for these APIs, please revise}

@@

\subsection{Contribution}

@@

\section{Conclusion and Future Work}
Deep Learning (DL) Libraries (e.g., \torch) provide the basic blocks
for creating AI-enabled applications, which are becoming very
popular. Several testing techniques have been proposed in the
literature to find bugs in these libraries. Unfortunately, the lack of
a dataset of reproducible bugs in those libraries poses an important
barrier to the proper evaluation of these techniques. \tname{} fills
the gaps. It includes a total of \numbugs\ across three major DL
libraries. We plan to continue expanding this dataset and to explore
automated approaches to extract patches from issue trackers and
``frontport'' them~\cite{hazimeh2020magma} to a single version of the
library to facilitate testing.

>>>>

\vspace{-1ex}
\subsection{Usage}
\label{sec:usage}

@@

The following script runs FreeFuzz all bugs associated with version
2.2.0 of \torch.  The command \CodeIn{run-tool} takes the library
version as an input, along with the name of the docker container
(already created), the name of the library, and the user-provided
script containing the commands to run the tool
(\CodeIn{run\_freefuzz\_docker.sh}. The script reports on output how
many bugs are reproducible with this library version were successfully
reproduced by the given tool.  Tool execution proceeds as
follows. First, a Docker container associated with the tool is created using
\CodeIn{install\_freefuzz\_docker.sh}. Next, a reproducible bug is tested using
the specified library version as input to verify the setup.
Following this, the preprocessing script (\CodeIn{preprocess.py}) is executed 
to extract error types and identify buggy APIs for the given library version.
The environment inside the Docker container is then updated to match the specified version, 
ensuring compatibility before running the fuzzing tool. Once execution is complete, a postprocessing 
script (\CodeIn{postprocess.py}) is run to analyze the execution log against the ground truth, 
determining whether the bugs were successfully reproduced.

@@

% \Fix{Abid: Added text to motivate adding support for these APIs, please revise}

@@

\subsection{Contributions}

@@

\section{Conclusion and Future Work}
Deep Learning (DL) Libraries (e.g., \torch) provide the basic blocks
for creating AI-enabled applications, which are becoming very
popular. Several testing techniques have been proposed in the
literature to find bugs in these libraries. Unfortunately, the lack of
a dataset of reproducible bugs in those libraries poses an important
barrier to the proper evaluation of these techniques. \tname{} fills
this gap. It includes a total of \numbugs\ across three major DL
libraries and provides an infrastructure to integrate fuzzers and
evaluate them. We plan to continue expanding this dataset and to
explore automated approaches to extract patches from issue trackers
and ``frontport'' them~\cite{hazimeh2020magma} to a single version of
the library to facilitate testing even further.
